Potential Novel Immunotarget Revealed in Mega Analysis of Colorectal Transcriptomes

### 2020-12-27 manuscript/main.tex
overhall to include validation of results

For validation of discovered associations, two independent cohorts were used.
The first (validation \#1) included paired end sequencing from 30 pairs of tumor and matched adjacent normal biopsies (i.e. 15 samples of both tissue phenotypes paired by subject).
The second (validation \#2) included single end sequencing from 275 colon biopsies of which NUMBER were healthy, NUMBER were tumor adjacent, and NUMBER were tumor.
An important characteristic of the discovery cohort and the validation \#2 cohort was the independence of all tumor and tumor adjacent samples.
To permit valid inference from regular linear models, only one tissue phenotype was used per subject.

@@

restabs <- list()
for (cohort in c("A", "B", "C")) {
    restabs[[cohort]] <- load_res_tables("herv", scope="hrv")
}

idx <- lapply(restabs, fun <- function(x1) {
    idx1 <- lapply(x1, fun <- function(x2) {
        a <- x2$padj < 0.05
        b <- x2$log2FoldChange > 0
        c <- a & b
        return(c)
    })
    return(idx1)
})

l <- list()
for (n1 in names(restabs)) {
    l[[n1]] <- list()
    for (n2 in names(restabs[[n1]])) {
        l[[n1]][[n2]] <- restabs[[n1]][[n2]][idx, "gene_id"]
    }
}

l <- lapply(restabs, fun <- function(x) {
    for (i in seq_len(length(x))) {
        x[[i]]
    }
})

tophervs <- restabs[["TUMvHLT"]][idx, "gene_id"]

cohort <- "A"
restabsA <- load_res_tables("herv", scope="hrv")
cohort <- "B"
restabsB <- load_res_tables("herv", scope="hrv")
cohort <- "C"
restabsC <- load_res_tables("herv", scope="hrv")

idxA <- lapply(restabsA, fun <- function(x) {
    a <- x$padj < 0.05
    b <- x$log2FoldChange > 0
    c <- a & b
    return(c)
})

conds[[1]] <- restabs[["NATvHLT"]]$padj < 0.05
conds[[2]] <- restabs[["NATvHLT"]]$log2FoldChange > 0

>>>>

For validation of discovered associations, two independent cohorts were used.
The first (independent cohort \#1) included single end sequencing from 275 colon biopsies of which NUMBER were healthy, NUMBER were tumor adjacent, and NUMBER were tumor.
The second (independent cohort \#2) included paired end sequencing from 30 pairs of tumor and matched adjacent normal biopsies (i.e. 15 samples of both tissue phenotypes paired by subject).
An important characteristic of the discovery cohort and independent cohort \#1 was the independence of all tumor and tumor adjacent samples.
To permit valid inference from regular linear models, only one tissue phenotype was used per subject.

@@
